### 2022-06-29 manuscript/manuscript.Rmd
add a reference to Smedsgaard 2005

These magnitude increases in data volume require the development of computationally efficient processing routines, especially for processing large sample sets.
Spectral artefacts such as Gibbs oscillations, that are common in Fourier Transform based MS, adds further complexity [@marshall2008].
Similarly, the alignment of mass spectra between samples can also make processing difficult, especially in analytical runs containing many samples [@draper2013].
Approaches such as the *proFIA* R package have already attempted to overcome some of these challenges [@delabriere2017].

@@

standards_base_peak_matches %>%
  split(.$`Molecular formula`) %>% 
  map(~{.[1,]}) %>% 
  bind_rows() %>% 
  arrange(desc(Abundance)) %>%
  .[1:10,] %>%
  arrange(Metabolite) %>% 
  mutate_at(vars(purity,centrality,`PPM error`),signif,digits = 3) %>%
  mutate_at(vars(Abundance),round,digits = 0) %>%
  rename(Compound = Metabolite,
         Purity = purity,
         Centrality = centrality,
         `$\\Delta$ ppm` = `PPM error`) %>%
  mutate(Adduct = Adduct %>% 
           str_replace_all(']1-',']$^{1-}$') %>% 
           str_replace_all(coll(']1+'),']$^{1+}$'),
         `Molecular formula` = str_replace_all(`Molecular formula`,
                                             "([0-9]+)", 
                                             "$_{\\1}$"
                                               )) %>% 
  kable(format = 'latex',
      booktabs = TRUE,
      linesep = '',
      caption = 'Extracted accurate \\textit{m/z} base peaks for 0.01 amu bins detected for compounds in the mix of chemical standards. The top ten most abundant base peaks are shown. For a full list of detected peaks see Supplementary Table S4.',
      escape = FALSE,) %>%
  kable_styling(font_size = 10,
                latex_options = 'HOLD_position') %>% 
  column_spec(1,'3cm') %>% 
  column_spec(2,'2cm') %>%
  column_spec(3,'1.3cm') %>%
  column_spec(4,'1.6cm') %>%
  column_spec(5,'1.6cm') %>%
  column_spec(6,'1.4cm') %>%
  column_spec(7,'1cm') %>%
  column_spec(8,'1cm') %>%
  column_spec(9,'1cm') 
```

>>>>

These magnitude increases in data volume require the development of computationally efficient processing routines, especially for processing large sample sets.
Spectral artefacts such as Gibbs oscillations, that are common in Fourier Transform based MS, adds further complexity [@marshall2008].
Similarly, the alignment of mass spectra between samples can also make processing difficult, especially in analytical runs containing many samples [@draper2013].
Approaches such as that of @smedsgaard2005 and the *proFIA* R package have already attempted to overcome some of these challenges [@delabriere2017].

@@

standards_base_peak_matches %>%
  split(.$`Molecular formula`) %>% 
  map(~{.[1,]}) %>% 
  bind_rows() %>% 
  arrange(desc(Abundance)) %>%
  .[1:10,] %>%
  arrange(Metabolite) %>% 
  mutate_at(vars(purity,centrality,`PPM error`),signif,digits = 3) %>%
  mutate_at(vars(Abundance),round,digits = 0) %>%
  rename(Compound = Metabolite,
         Purity = purity,
         Centrality = centrality,
         `$\\Delta$ ppm` = `PPM error`) %>%
  mutate(Adduct = Adduct %>% 
           str_replace_all(']1-',']$^{1-}$') %>% 
           str_replace_all(coll(']1+'),']$^{1+}$'),
         `Molecular formula` = str_replace_all(`Molecular formula`,
                                             "([0-9]+)", 
                                             "$_{\\1}$"
                                               )) %>% 
  kable(format = 'latex',
      booktabs = TRUE,
      linesep = '',
      caption = 'Extracted accurate \\textit{m/z} base peaks for 0.01 amu bins detected for compounds in the mix of chemical standards. The top ten most abundant base peaks are shown. For a full list of detected peaks see Supplementary Table S4.',
      escape = FALSE,
      digits = 8) %>%
  kable_styling(font_size = 10,
                latex_options = 'HOLD_position') %>% 
  column_spec(1,'3cm') %>% 
  column_spec(2,'2cm') %>%
  column_spec(3,'1.3cm') %>%
  column_spec(4,'1.6cm') %>%
  column_spec(5,'1.6cm') %>%
  column_spec(6,'1.4cm') %>%
  column_spec(7,'1cm') %>%
  column_spec(8,'1cm') %>%
  column_spec(9,'1cm') 
```
